\section{Project Structure}

\subsection{System Architecture}
% TODO @ozneroL541
The system follows a distributed replica-based architecture implemented using 
Akka actors, where each replica maintains a local copy of the shared positions 
database and communicates exclusively through asynchronous immutable messages. 
Client actors can contact any replica to issue read or write requests. 
Read operations are served immediately using the replica's local state, 
while write requests are forwarded to a replica whose act as coordinator. 
The coordinator executes a quorum-based two-phase commit protocol 
by first broadcasting an \texttt{UPDATE} message, collecting acknowledgements from a 
strict majority of replicas, and then disseminating a \texttt{WRITEOK} message that 
commits the update at all replicas.
To ensure fault tolerance, the coordinator periodically send an heartbeat message to 
all replicas, which monitor the its state in order to detect its crash.
If the coordinator crashes, a ring-based election protocol selects 
the most up-to-date replica as the new coordinator.
Once the coordinator is elected, it initiates a synchronization phase
sending its updated history to all replicas, which synchronizes any missing
updates before resuming normal operation.
Since the message passing is FIFO and reliable, this architecture guarantees
sequential consistency, total ordering of updates, quorum-based fault tolerance, 
and eventual convergence of all correct replicas despite node failures.

\subsection{Code Structure}
% TODO @ozneroL541
The project is structured around the Akka actor model, 
with separate classes for system initialization, communication, client, 
and replica management.
The central component is the \texttt{Replica} class, which extends \texttt{AbstractReplica} 
and implements the distributed protocol: it stores the replicated data and update history, 
processes read and write requests, coordinates updates through acknowledgements and 
quorums, detects failures using heartbeats and timeouts, and manages coordinator elections 
and state synchronization after a crash.
The \texttt{Client} class extends \texttt{AbstractClient} and provides act as a users 
which contact the replicas by sending read and write requests, scheduling 
operation-specific timeouts, receiving acknowledgements, cancelling completed timeout tasks, 
and reporting successful or failed operations through the callback mechanisms defined by 
its abstract superclass.
Supporting classes further separate concerns: \texttt{NetworkChannel} simulates FIFO 
network communication with random latency, \texttt{UpdateClock} provides logical 
ordering for updates, and \texttt{Logger} centralizes diagnostic output.

\subsection{Our Assumptions}
We assume that if a replica crashes after receiving a write request from a 
client,the operation will time out from the client's perspective. 
Nevertheless, the write operation will still be processed and applied by the 
coordinator and the remaining correct replicas following the election of a new coordinator.
Furthermore, we assume that a newly elected coordinator cannot crash during the 
synchronization phase (i.e., while broadcasting the \texttt{Synchronization} message)
% TODO @ozneroL541
