\section{System Design}\label{sec:sys-design}
% Define protocols specific choices
\subsection{Two-phase Broadcast Protocol}
The implemented two-phase broadcast protocol allows any client to issue \texttt{WriteRequest} or \texttt{ReadRequest} messages to any replica within the system.
Upon receiving a request, the replica processes it differently depending on its type. If it is a \texttt{ReadRequest}, the replica immediately replies to the client with the requested value.
If, instead, it's a \texttt{WriteRequest}, the replica stores the received message in a pending writes queue and forwards the request to the system's coordinator. This queue allows the replica to keep track of uncompleted write operations requested to it directly by a client. 
Once the write operation is eventually completed, the replica utilizes this queue to forward a \texttt{WriteResult} message back to the client.
When the coordinator receives the forwarded write request, it first sends an acknowledgment to the replica that forwarded it and then it broadcasts an \texttt{UpdateMessage} to all replicas in the system. This message contains both the \texttt{WriteRequest} and the unique identifier,  consisting of an \texttt{epoch} $e$ and a \texttt{sequence number} $i$, assigned to the request by the coordinator.
The coordinator then waits to receive an acknowledgment for the update from a quorum, which must consist of at least a strict majority of the system's replicas. 
It is important to note that, in this context, the coordinator also acts as a standard replica; therefore, it sends the \texttt{UpdateMessage} to itself and counts its own internal acknowledgment as valid for reaching the required quorum.
Every replica that receives an \texttt{UpdateMessage} inserts the \texttt{WriteRequest} into a local hash table, using the coordinator-assigned identifier as the key. After storing the message, the replica sends an acknowledgment back to the coordinator.
Upon successfully collecting acknowledgments from a valid quorum, the coordinator broadcasts a \texttt{WriteOK} message to all replicas in the system.
Once a replica receives the \texttt{WriteOK} message, it executes the write operation only if the identifier associated with the request is greater than the identifier of the last executed write.
After the write is successfully applied, the replica updates its write history. This history is maintained via a hash table that associates each identifier with its corresponding \texttt{WriteRequest} message.
Finally, the replica removes the newly executed write from the local hash table used while handling the \texttt{UpdateMessage}. If the write was also present in the pending writes queue, then the replica sends a \texttt{WriteResult} message to the originating client.

\subsection{Crash Detection}
In order to detect when the coordinator has crashed, it periodically sends an
\texttt{Heartbeat} message in broadcast to all replicas in the system.
Each replica maintains a timer that is reset every time it receives a 
\texttt{Heartbeat} message from the coordinator.
If a replica's timer expires without receiving a heartbeat, 
it assumes that the coordinator has crashed and initiates the leader election protocol 
to select a new coordinator.
If the replica whose timer has expired is the current coordinator, 
it will send an \texttt{Heartbeat} message to all replicas in the system 
and set its own timer to half of the standard timeout value to trigger it 
before the timer of the other replicas.

\subsection{Election Protocol}
The election protocol is based on a logical ring topology, 
where replicas are arranged by their unique identifiers in a circular manner.
When a replica detects that the coordinator has crashed, 
it sends an \texttt{Election} message to its successor in the ring.
The \texttt{Election} message contains the identifier of the replica 
that initiated the election and a \texttt{Map} which contains the \texttt{id}
of all replicas that have participated in the election so far and their
\texttt{UpdateClock}, which is a logical clock that tracks the updates.
When the \texttt{Election} message reaches a replica, it checks whether it 
should process it and if does it adds its own identifier and 
\texttt{UpdateClock} to the \texttt{Map} and forwards the message to 
its successor in the ring and an Acknowledgment message to the replica 
that sent the \texttt{Election} message before it.
When sending the \texttt{Election} message, the replica sets a timer 
to wait for an acknowledgment from its successor.
If the timer expires without receiving an acknowledgment,
the replica assumes that its successor has crashed and sends the 
\texttt{Election} message to the next replica in the ring.
When the \texttt{Election} message returns to the replica that initiated the election
or to a replica that has already participated in the election,
it determines the new coordinator by selecting the replica with the 
most recent \texttt{UpdateClock} (or the highest identifier in case of a tie) 
from the \texttt{Map} contained in the \texttt{Election} message and 
sends a \texttt{CoordinatorElected} message which is propagated around the ring 
as before, until it reaches the new coordinator.
When that message reaches the new coordinator, it sends the 
\texttt{Synchronization} message to all replicas in the system, 
which contains the updates that need to be applied to bring all replicas up to date 
with the new coordinator's state.
The \texttt{Synchronization} message will not be processed by the replicas until 
they have received the \texttt{CoordinatorElected} message.

\subsection{Synchronization Protocol}
Once a new coordinator is elected, it must perform a series of operations before restoring the system to the default state.
First, it will broadcast a \texttt{Heartbeat} message to all replicas in the system. It is crucial that this is one of the coordinator's initial actions to prevent replicas from timing out due to a lack of \texttt{Heartbeat} messages, which would trigger a new, erroneous election.
Once the initial \texttt{Heartbeat} messages have been dispatched, the coordinator must ensure that all uncompleted write messages are properly processed. There are two categories of these write messages:
\begin{itemize}
    \item Messages that the previous coordinator has already assigned an identifier to.
    \item Messages received by a replica but never successfully forwarded to the coordinator, meaning they do not yet have an assigned identifier.
\end{itemize}
Regarding the first category, given the design of the leader election protocol, the newly elected coordinator is guaranteed to be the replica with the most up-to-date knowledge of these messages. Therefore, it will first put these messages into its own history,
handling any necessary \texttt{WriteResult} messages to be sent back to the clients. Once the history is updated, it will filter and extract from it all the updates subsequent to the last update executed by the least up-to-date replica, and broadcast these messages via a \texttt{Synchronization} message.
Upon receiving the \texttt{Synchronization} message, each replica executes all the \texttt{WriteRequests} and updates its own history. Then, they clean their local hash tables and pending writes queue. If some write messages were present in their pending writes queue, the replica will then forward a \texttt{WriteResult} message to the client that initially issued the request.
Once the history is fully synchronized, the replica iterates through all \texttt{WriteRequest} messages waiting to be forwarded and sends them to the new coordinator. The coordinator will then assign them a new identifier and process them as standard new messages.
Finally, once all replicas have received the \texttt{Synchronization} message, applied the necessary updates, and forwarded any pending \texttt{WriteRequest} messages, the system officially returns to a normal operational state.
